A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

Regarding the proposed algorithm, \malg, it has been obtained an upload bandwidth usage reduction of 63.51\% and 33.58\%, respectively compared to the circular area of interest and the field of view based algorithms. The maximum upload bandwidth usage was also reduced, decreasing 63.51\% and 33.58\%, comparing to the same algorithms. Table \ref{tab_summary} shows the percentage of economy-wide average, maximum and average banda with the algorithm \ malg compared with other algorithms presented.

No que diz respeito ao algoritmo proposto \malg, obteve-se uma redução de uso médio de largura de banda de envio de 63.51\% e 33.58\%, comparado respectivamente com o algoritmo de área de interesse circular e baseado em ângulo de visão. Reduziu-se também o pico de utilização em 52.03\% e 33.10\%, comparado com os mesmos algoritmos. Na tabela \ref{tab_summary}, são mostrados os percentuais médios de economia de largura de banda máxima e média com o algoritmo \malg, em relação aos outros algoritmos apresentados.

\begin{table}[ht]
\caption{Economia de largura de banda com o algoritmo \malg}
\centering
  \begin{tabular}{ c | c c c c }  
    \hline
   	Utilização & \noaoi & \circleaoi & \circleat & \fov \\ \hline
		Máxima	&	60.10\%	&	52.03\%	&	24.81\%	&	33.10\%	\\
		Média	&	81.64\%	&	63.51\%	&	37.48\%	&	33.58\%	\\
	\hline
  \end{tabular}
\label{tab_summary}
\end{table}

Observou-se também que os valores médio e máximo observados diferem, mesmo quando não é utilizado nenhum algoritmo de gerenciamento de interesse, ou seja, o cliente recebe atualizações de estado de todas as entidades presentes no jogo, com a freqüência normal. Além disso, com 200 avatares no ambiente, com estado de 100 bytes, cuja atualização é enviada a cada 250 ms, o servidor deveria alocar 199$\times$100$\times$4 bytes/s para cada cliente, ou seja, 79600 bytes/s. No entanto, observou-se que a utilização máxima e média, com 200 avatares presentes e nenhum gerenciamento de interesse, foi de 77600 e 76458, respectivamente. Isso acontece porque o ns-2 é um simulador de eventos discreto, e o servidor simulado foi programado para checar o schedule de envios a cada 10 ms. Em conseqüência disto, cada atualização de estado pode ter tido seu intervalo aumentado em até 10 ms, o que explica os valores encontrados.

\section{Conclusion}
\label{conclusion}
Foi apresentado um algoritmo de gerenciamento de interesse, o \malg, cuja idéia principal é adaptar a freqüência de atualização de estado das entidades do jogo de acordo com sua relevância para o cliente que receberá as atualizações. O formato da área de interesse utilizada pelo algoritmo \malg{} consiste em um setor de círculo, correspondente ao campo de visão do jogador, mais um círculo de raio menor, que corresponde à área próxima ao avatar daquele jogador. O objetivo deste círculo menor é o de manter o estado naquela região, que é considerada crítica, o mais atualizado possível. Somando-se essas características, chegamos a um algoritmo que obteve redução da utilização máxima da banda de envio do servidor de 52.03\% e 33.10\%, comparados com o gerenciamento de interesse baseado em círculo e em campo de visão, respectivamente, e de 63.51\% e 33.58\% de utilização média, comparados com os mesmos algoritmos.

>>>>

Regarding the proposed algorithm, \malg, it has been obtained an upload bandwidth usage reduction of 63.51\% and 33.58\%, compared to the circular area of interest and the field of view based algorithms, respectively. The maximum upload bandwidth usage was also reduced, decreasing 52.03\% and 33.10\%, compared to the same algorithms. Table \ref{tab_summary} shows the maximum and average bandwidth saving percentage of the \malg\ algorithm compared to the other techniques. For example, the maximum bandwidth utilization with \malg\ is 24.81\% less than with a circular area of interest based algorithm with update frequency attenuation.

\begin{table}[ht]
\caption{Bandwidth saving with \malg\ algorithm}
\centering
  \begin{tabular}{ c | c c c c }  
    \hline
   	Usage & \noaoi & \circleaoi & \circleat & \fov \\ \hline
		Maximum	&	60.10\%	&	52.03\%	&	24.81\%	&	33.10\%	\\
		Average	&	81.64\%	&	63.51\%	&	37.48\%	&	33.58\%	\\
	\hline
  \end{tabular}
\label{tab_summary}
\end{table}

It was also observed that the average and maximum observed values differ, even when there is no algorithm used to manage interest, that is, the client receives state updates of all entities in the game, with maximum frequency. With 200 avatars in the environment, 100 bytes state update packet size and 250 ms normal update interval, the server should be using 80000 bytes per second - 200 $ \ times $ 100 $ \ times $ 4 - for each client. However, it was observed that the maximum and average usage, with 200 avatars present and no interest management, was 77600 and 76458, respectively. This happens because ns-2 is a discrete event simulator, and the simulated server was programmed to check the update schedule every 10 ms. As a result of this, each state update may have had its interval increased by up to 10 ms, which explains the values found.

\section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to adapt the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest shape consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most updated possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average upload bandwidth utilization by the server also decreased 63.51\% and 33.58\%, compared to the same algorithms.
